Trifunctional Phosphatidic Acid

### 2025-08-29 BioinformaticsApplicationNote/Bioinformatics_ReviewerResponseLetter.qmd

---

format: 
  docx:
    reference-doc: custom-reference-doc.docx
  # pdf: 
  #   latex-engine: pdflatex
---

Dear Dr. Hutchins,

We thank you again for the opportunity to address the reviewers' comments on our first draft of our manuscript -- we have included with this letter an updated mansucript draft and have incorporated as many of their suggestions as we could feasibly achieve in the Lipid Interactome site.

We are grateful for thought that the reviewers put into their comments. We interpreted several throughlines in their comments: 1. Requests for additional metadata about study methodology and the incorporation of additional data (e.g. accession numbers in addition to gene names), 2. Requests for additional information about data submission, processing, and harmonization methods, 3. Requests for an automated/scalable data submission pipeline, and 4. The identification of typographical errors, malformed links, and bugs in the site.

Many of these points have been addressed directly either in the text or on the Lipid Interactome repository. For example, the broken links and typographical errors in figure captions have been addressed, additional cell line information has been added to our *Comparing the Enriched Hits of Different Probes* Shiny app, we have included of accession number to convey crucial information about isoform identifications in addition to using gene name to identify hits (where possible in the original datasets; the authors of Hoglinger 2017 have been unresponsive and we do not have the accession number data for their results) and clarification about the qualitative nature of the comparisons displayed in the Shiny app. We have additionally provided links to download the R scripts were used to "wrangle" the submitted data to the formats that our data visualization functions accept.

We highly concur with the reviewers' request for an automated data submission system. At present, this site has been built, managed, and maintained through the efforts of a single individual and we do not currently have the resources to overhaul the site to sufficiently incorporate these needs; we are seeking additional funding from the Open Oregon Educational Resources and the Code for Science and Society programs to support this individual in building these functionalities into our site. It is a long-term vision of our group to build a more scalable version of this repository which requires minimal manual management and enables automated data submission. However, we further feel that the underlying architecture of this repository is independent of its utility to the external lipid research community.

### 2025-08-29 404.qmd
removed naughty docx formatting
Minor updates
Added template files for the individual studies
Addressing more of the reviewer comments, accession numbers mostly

---
---

@@

<h2 style> Ooops! </h2>

@@

<b> The page you're looking for doesn't (perhaps it was moved or renamed, or perhaps the site is still under construction and you can check back soon).</b>

>>>>

---
title: "404 -- Page Not Found   "
---

@@

<h1 style> Ooops! </h1>

@@

<b> The page you're looking for doesn't exist (perhaps it was moved or renamed, or perhaps the site is still under construction and you can check back soon).</b>

### 2025-08-29 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Addressing more of the reviewer comments, accession numbers mostly

While there are numerous ways to quantify the mass spectrometry (MS) data, the majority of studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using data-dependent acquisition techniques, such as Tandem Mass Tagging[@thompsonTandemMassTags2003]. These datasets include those reported by Farley et al. (2024), Farley et al. (2024), and Thomas et al. (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025]. Some studies have also featured quantitative MS analysis using stable isotope labeling of amino acids in cell culture (SILAC), which also enables extraction of key data described below[@chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022]. Correspondingly, the ideal data structure for incorporation into our repository will include the following:

:::{.border}

| Gene name | [Uniprot accession](https://www.uniprot.org/help/accession_numbers) | logFC | p value |  AveExpr   |  FDR   |
|:---------- | :------: |:------------------------:|:-------:|:----------:|:------:|
| GeneA     | P80723 |           1.2            |  0.001  | 1.0x10^18^ | 0.0001 |
| GeneB     | P32004 |          0.1            |   0.6   | 1.0x10^5^  | 0.005  |
| ...       | ... |          ...            |   ...   |    ...     |  ...   |
: **Example data table for smooth incorporation into Lipid Interactome.** ***Column descriptions:*** *Gene name*: The identifier for genes identified in the dataset (or Accession Number). *Uniprot accession*: Stable identifiers of UniProtKB entries; integrates species and isoform data on the identified protein. *Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods. *p value*: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing. *AveExpr*: An averaged value of the m/z ion intensity of the Experimental condition and Control condition used for the enrichment value (used to prepare MA plots for quality control). *FDR*: False-discovery rate of protein identification. {#tbl-1 .striped}

:::
</br>

**We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison.**

@@

@@

Designed as a continuously expanding repository, the Lipid Interactome will evolve alongside advances in lipid probe technologies and interactomics. Future iterations will incorporate validation studies for each lipid probe, offering researchers a dedicated space to compare findings across experimental contexts. This functionality will not only reduce redundancy in experimental design but also strengthen the reproducibility and biological interpretation of lipid interactome research. To support this vision, we invite researchers to contribute their datasets via our [Data Submission page](https://lipidinteractome.org/contactus/datasubmission), fostering a collaborative and transparent approach to lipid biology.

@@

GG designed, implemented, and wrote the majority of the LipidInteractome repository and manuscript. FS wrote the data analysis section of the repository, provided significant intellectual contribution to the repository design, and edited the manuscript. AN provided substantial editing of the repository and manuscript. JMB edited the manuscript and contributed data to the repository. CS and FT provided significant intellectual contribution and text editing of the repository and manuscript and oversaw the site development.

>>>>

While there are numerous ways to quantify the mass spectrometry (MS) data, the majority of studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using data-dependent acquisition techniques, such as Tandem Mass Tagging[@thompsonTandemMassTags2003]. These datasets include those reported by Farley et al. (2024), Farley et al. (2024), and Thomas et al. (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025]. Some studies have also featured quantitative MS analysis using stable isotope labeling of amino acids in cell culture (SILAC), which also enables extraction of key data described below[@chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022]. Correspondingly, the ideal data structure for incorporation into our repository will contain the information shown in @tbl-dataStructure.

:::{.border}
| Gene name | [Uniprot accession](https://www.uniprot.org/help/accession_numbers) | logFC | p value |  AveExpr   |  FDR   |
|:---------- | :------: |:------------------------:|:-------:|:----------:|:------:|
| GeneA     | P80723 |           1.2            |  0.001  | 1.0x10^18^ | 0.0001 |
| GeneB     | P32004 |          0.1            |   0.6   | 1.0x10^5^  | 0.005  |
| ...       | ... |          ...            |   ...   |    ...     |  ...   |
: **Example data table for smooth incorporation into Lipid Interactome.** ***Column descriptions:*** *Gene name*: The identifier for genes identified in the dataset (or Accession Number). *Uniprot accession*: Stable identifiers of UniProtKB entries; integrates species and isoform data on the identified protein. *Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods. *p value*: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing. *AveExpr*: An averaged value of the m/z ion intensity of the Experimental condition and Control condition used for the enrichment value (used to prepare MA plots for quality control). *FDR*: False-discovery rate of protein identification. {#tbl-dataStructure .striped}
:::
</br>

**We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison. As proteomics techniques have improved rapidly in recent years, we have done our best to incorporate all data structures into this repository**

@@

At present, we are accepting datasets as analyzed by the original researchers, including protein identifications, enrichment quantification, and the results of statistical testing. We are working to incorporate comprehensive details of the analysis workflow in each study.

@@

Designed as a continuously expanding repository, the Lipid Interactome will evolve alongside advances in lipid probe technologies and interactomics. Ongoing efforts seek to incorporate enhanced scalability of this site, more robust data storage methods, and automated data submission. These functionalities will improve the utility of this repository, enabling applications such as machine learning for pattern recognition as the site grows. Future iterations will incorporate validation studies for each lipid probe, offering researchers a dedicated space to compare findings across experimental contexts. This functionality will not only reduce redundancy in experimental design but also strengthen the reproducibility and biological interpretation of lipid interactome research.

To support this vision, we invite researchers to contribute their datasets via our [Data Submission page](https://lipidinteractome.org/contactus/datasubmission). Using the FAIR data principles, we hope to foster a collaborative and transparent approach to lipid biology.

@@

GG designed, implemented, and wrote the majority of the Lipid Interactome repository and manuscript. FS wrote the data analysis section of the repository, provided significant intellectual contribution to the repository design, and edited the manuscript. AN provided substantial editing of the repository and manuscript. JMB edited the manuscript and contributed data to the repository. CS and FT provided significant intellectual contribution and text editing of the repository and manuscript and oversaw the site development.

### 2025-08-29 ContactUs/about.tex
Addressing more of the reviewer comments, accession numbers mostly

\begin{tcolorbox}[enhanced jigsaw, bottomtitle=1mm, coltitle=black, arc=.35mm, rightrule=.15mm, colback=white, breakable, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, toprule=.15mm, opacitybacktitle=0.6, toptitle=1mm, titlerule=0mm, left=2mm, leftrule=.75mm, opacityback=0]

>>>>

\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, coltitle=black, colframe=quarto-callout-note-color-frame, breakable, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, colbacktitle=quarto-callout-note-color!10!white, colback=white, leftrule=.75mm, titlerule=0mm, bottomtitle=1mm, toptitle=1mm, arc=.35mm, rightrule=.15mm, left=2mm, toprule=.15mm]

### 2025-08-29 IndividualStudies/AT_2025.qmd
Addressing more of the reviewer comments, accession numbers mostly

```{r setup, echo=FALSE, include=FALSE}

## intitialize libraries
library(here)
library(dplyr)
library(duckplyr)
library(ggplot2)
library(ggrepel)
library(emojifont)
library(dplyr)
library(tidyr)
library(docstring)
library(clusterProfiler)
library(org.Hs.eg.db)
library(enrichplot)
library(igraph)
library(ggtangle)
library(stringr)
library(crosstalk)
library(plotly)
library(grid)
library(readr)
library(rmarkdown)
library(gt)
library(DT)
library(heatmaply)
library(ggvenn)
library(scales)
library(htmltools)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

@@

:::{.border}
```{r, echo=FALSE}

@@

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 10))

@@

## intitialize libraries
library(here)
library(dplyr)
library(duckplyr)
library(ggplot2)
library(ggrepel)
library(emojifont)
library(dplyr)
library(tidyr)
library(docstring)
library(clusterProfiler)
library(org.Hs.eg.db)
library(enrichplot)
library(igraph)
library(ggtangle)
library(stringr)
library(crosstalk)
library(plotly)
library(grid)
library(readr)
library(rmarkdown)
library(gt)
library(DT)
library(heatmaply)
library(ggvenn)
library(scales)
library(htmltools)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

@@

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 10))

>>>>

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

here()

## Opening the source file for the ggplot custom theme
source(here("Resources/ggplot_styles.R"))

@@

:::{.border}
```{r, echo=FALSE}
# Slight cleanup for presenting in the datatable
data <- data |>
  mutate(logFC = signif(logFC, digits=3)) |>
  mutate(pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation) |>
  select(-Protein.Description)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))
```

@@

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))

### 2025-08-29 IndividualStudies/SF_2024.qmd
Addressing more of the reviewer comments, accession numbers mostly

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name","Protein ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Average Expression", "FDR"))

>>>>

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name","Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Average Expression", "FDR"))

### 2025-08-29 IndividualStudies/SF_2024_B.qmd
Addressing more of the reviewer comments, accession numbers mostly

## Displays the reactive dataframe
datatable(data_reactive,
         options = list(pageLength = 10))

>>>>

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name","Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Average Expression", "FDR"))

### 2025-08-29 IndividualStudies/SK_2024.qmd
Addressing more of the reviewer comments, accession numbers mostly

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a p-value < 0.05 and a fold-change > 2 (log2FC > 1) for the bf-GPI versus control probe, and 'enriched hits' are defined as proteins with a p-value < 0.05 and a fold change of at least 4-fold (log2FC >2) for the bf-GPI versus control probe", 
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Gene ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value"))

>>>>

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value"))

```
'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a p-value < 0.05 and a fold-change > 2 (log2FC > 1) for the bf-GPI versus control probe, and 'enriched hits' are defined as proteins with a p-value < 0.05 and a fold change of at least 4-fold (log2FC >2) for the bf-GPI versus control probe
:::

### 2025-08-29 IndividualStudies/WY_2021.qmd
Addressing more of the reviewer comments, accession numbers mostly

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3)) |>
  mutate(pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed.",
          options = list(pageLength = 10),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value"),
                         rownames=FALSE)

>>>>

data <- data |>
  dplyr::select(gene_name, Accession, LipidProbe, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3)) |>
  mutate(pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed.",
          options = list(pageLength = 10),
                         colnames = c("Gene Name", "Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value"),
                         rownames=FALSE)

### 2025-08-29 LipidProbe/Glycosylphosphatidylinositol.qmd
Addressing more of the reviewer comments, accession numbers mostly

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

@@

data <- data |>
  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation, -logFC)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 10),
                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))

>>>>

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))
```

@@

data <- data |>
  dplyr::select(gene_name, Accession, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation, -logFC)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value"))

### 2025-08-29 LipidProbe/N-Acylphosphatidylethanolamine.qmd
Spent a long time learning about custom divs, applied a new one for cell types
Addressing more of the reviewer comments, accession numbers mostly

---
title: "Bifunctional N-Acylphosphatidylethanolamine"
subtitle: "NAPE"
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

@@

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. logFC ratios are median normalized. \"Num Replicate IDs\" denotes the number of replicates in which the protein was identified. As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01. \"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
                         rownames=FALSE)

@@

>>>>

---
title: "Bifunctional N-Acylphosphatidylethanolamine"
subtitle: "NAPE"
format: 
  html:
    embed-resources: false
---

@@

data <- data |>
  dplyr::select(gene_name, gene_ID, hit_annotation, logFC, pvalue, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

@@

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
                         rownames=FALSE)

@@

This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. logFC ratios are median normalized. \"Num Replicate IDs\" denotes the number of replicates in which the protein was identified. As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01. \"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.

### 2025-08-29 LipidProbe/PhosphatidicAcid.qmd
Spent a long time learning about custom divs, applied a new one for cell types
Addressing more of the reviewer comments, accession numbers mostly

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

@@

```{r setup, echo=FALSE, include=FALSE}

## intitialize libraries
library(here)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

```{r, echo=FALSE, include=FALSE}

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
# Read the data to a df

# AT_2025 <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
# 	filter(LipidProbe == "PA")

# write.csv(AT_2025, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")

data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

@@

:::
:::

#### Gene Ontology Analysis

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
:::::

@@

@@

data <- data |>
  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation, -logFC)

@@

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation,
                  inline="true")
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))

@@

{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download">}}

@@

>>>>

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
format: 
  html:
    embed-resources: false
---

@@

:::{.cells collapse="true"}
::::{.cells-header}
Membrane Fraction
::::
::::{.cells-container}

@@

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

here()

## Opening the source file for the ggplot custom theme
source(here("Resources/ggplot_styles.R"))

# Read the membrane data to a df
data <- readr::read_csv(here("LipidProbe/DataSets/PA_membrane_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

@@

:::
::::
:::

<!-- 
#### Gene Ontology Analysis

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
::::: -->

@@

# Here is the code to make the filterable lists shown in the crosstalk table below
# Slight cleanup for presenting in the datatable
data <- data |>
  mutate(logFC = signif(logFC, digits=3)) |>
  mutate(pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation) |>
  select(-Protein.Description)

@@

@@

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))

@@

{{< downloadthis DataSets/PA_membrane_HeLa_AT_2025.csv dname="PA_membrane_HeLa_AT_ChemComm_download">}}

@@

:::{.cells collapse="true"}
::::{.cells-header}
Cytosolic Fraction
::::
::::{.cells-container}

```{r setup2, echo=FALSE, include=FALSE}

# Read the membrane data to a df
data <- readr::read_csv(here("LipidProbe/DataSets/PA_cytosol_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

MAStandard(data)

:::
::::
:::

# Here is the code to make the filterable lists shown in the crosstalk table below
# Slight cleanup for presenting in the datatable
data <- data |>
  mutate(logFC = signif(logFC, digits=3)) |>
  mutate(pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation) |>
  select(-Protein.Description)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))

{{< downloadthis DataSets/PA_cytosol_HeLa_AT_2025.csv dname="PA_cytosol_HeLa_AT_ChemComm_download">}}

::::
:::
